The Calculus of Linear Constructions

### 2021-10-12 writing/draft1.tex
draft

  \begin{lemma}
    Parallel reduction satisfies the diamond property. If $m \pstep m_1$ and $m \pstep m_2$ then there exists $m'$ such that $m_1 \pstep m'$ and $m_2 \pstep m'$.
  \end{lemma}

  \begin{corollary}
    The transitive reflexive closure of parallel reduction is confluent. If $m \pstep^* m_1$ and $m \pstep^* m_2$ then there exists $m'$ such that $m_1 \pstep^* m'$ and $m_2 \pstep^* m'$.
  \end{corollary}

@@

  \begin{theorem}
    Weakening. If $\Gamma \vdash m \stype{s} A$ is a valid, then for any $x \notin \Gamma$, judgment $\Gamma, x \utype B \vdash m \stype{s} A$ is derivable.
  \end{theorem}

@@

  \begin{lemma}
    Substitution. For $\Gamma_1, x \stype{s} A \vdash m \stype{t} B$ and $\Gamma_2 \vdash v \stype{s} A$, if $\mrg{\Gamma_1}{\Gamma_2}{\Gamma}$ is defined for some $\Gamma$, then $\Gamma \vdash [v/x]m \stype{t} [v/x]B$.
  \end{lemma}

@@

  \begin{theorem}
    Regularity. For any context $\Gamma$, term $m$, type $A$, and sort $s$, if $\Gamma \vdash m \stype{s} A$ is a valid judgment, then there exists some level $i$ such that $\overline{\Gamma} \vdash A \utype s_i$.
    \label{regularity}
  \end{theorem}

@@

  \begin{theorem}
    Subject reduction. For $\Gamma \vdash m \stype{s} A$, if $m \pstep n$ then $\Gamma \vdash n \stype{s} A$.
  \end{theorem}

@@

  \begin{lemma}
    Narity. If $\Gamma \vdash m \stype{s} A$ is a valid judgment, for any $x \notin \Gamma$, there is $occurs(x, m) = 0$.
  \end{lemma}

@@

  \begin{theorem}
    Linearity. If $\Gamma \vdash m \stype{s} A$ is a valid judgment, for any $(x \ltype B) \in \Gamma$, there is $occurs(x, m) = 1$.
  \end{theorem}

@@

>>>>

  \begin{lemma} Parallel reduction satisfies the diamond property. \\
    If $m \pstep m_1$ and $m \pstep m_2$ then there exists $m'$ such that $m_1 \pstep m'$ and $m_2 \pstep m'$.
  \end{lemma}

  \begin{corollary} The transitive reflexive closure of parallel reduction is confluent. \\ 
    If $m \pstep^* m_1$ and $m \pstep^* m_2$ then there exists $m'$ such that $m_1 \pstep^* m'$ and $m_2 \pstep^* m'$.
  \end{corollary}

@@

  \begin{lemma} Weakening. \\
    If $\Gamma \vdash m \stype{s} A$ is a valid, then for any $x \notin \Gamma$, judgment $\Gamma, x \utype B \vdash m \stype{s} A$ is derivable.
  \end{lemma}

@@

  \begin{lemma} Substitution. \\
    For $\Gamma_1, x \stype{s} A \vdash m \stype{t} B$ and $\Gamma_2 \vdash v \stype{s} A$, if $\mrg{\Gamma_1}{\Gamma_2}{\Gamma}$ is defined for some $\Gamma$, then $\Gamma \vdash [v/x]m \stype{t} [v/x]B$.
  \end{lemma}

@@

  \begin{theorem} Regularity. \\
     For any context $\Gamma$, term $m$, type $A$, and sort $s$, if $\Gamma \vdash m \stype{s} A$ is a valid judgment, then there exists some level $i$ such that $\overline{\Gamma} \vdash A \utype s_i$.
    \label{regularity}
  \end{theorem}

@@

  \begin{theorem} Subject reduction. \\
    For $\Gamma \vdash m \stype{s} A$, if $m \pstep n$ then $\Gamma \vdash n \stype{s} A$.
  \end{theorem}

@@

  \begin{lemma} Narity. \\
    If $\Gamma \vdash m \stype{s} A$ is a valid judgment, for any $x \notin \Gamma$, there is $occurs(x, m) = 0$.
  \end{lemma}

@@

  \begin{theorem} Linearity. \\
    If $\Gamma \vdash m \stype{s} A$ is a valid judgment, for any $(x \ltype B) \in \Gamma$, there is $occurs(x, m) = 1$.
  \end{theorem}

@@

  We prove the following lemma to commute erasure and substitution when needed.
  \begin{lemma} Erasure commutes with substitution. \\ 
    For any CLC terms $m$, $n$, and some variable $x$, $\erase{m[n/x]} = \erase{m}[\erase{n}/x]$. 
  \end{lemma}

  For the following theorem, we refer to the reductions of CLC as $\pstep_{\scriptscriptstyle \text{CLC}}$, and the reductions of CC$\omega$ as $\pstep_{\scriptscriptstyle \text{CC$\omega$}}$.
  \begin{theorem} \label{preserve} Erasure preserves reduction. \\
    For any CLC terms $m$, and $n$, if there is $m \pstep_{\scriptscriptstyle \text{CLC}} n$, then there is $\erase{m} \pstep_{\scriptscriptstyle \text{CC$\omega$}} \erase{n}$.
  \end{theorem}

  \begin{theorem} \label{embedding} Embedding. \\
    For any CLC context $\Gamma$, terms $m$, $A$, and sort $s$, if $\Gamma \vdash m \stype{s} A$ is a valid typing judgment in CLC, then $\erase{\Gamma} \vdash \erase{m} : \erase{A}$ is a valid a typing judgment in CC$\omega$.
  \end{theorem}

  If there exists some well typed CLC term with an infinite sequence of reductions, erasure will embed this term into a well typed CC$\omega$ term along with its infinite sequence of reductions. This is contradictory to the strong normalization property of CC$\omega$, thus this hypothetical term does not exist in CLC.

  \begin{theorem}
    Well-typed CLC terms are strongly normalizing.
  \end{theorem}
